long_ts

### 2019-08-03 SACTN_lts.Rmd
updating

save(SACTN_US, file = "Data/SACTN_US.RData")
```

@@

```{r}
#' # Or if one wants to calculate MCSs
res_clim <- ts2clm(SACTN_PN, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 10)
PN_MCS <- detect_event(res_clim, coldSpells = TRUE)

res_clim <- ts2clm(SACTN_LB, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 10)
LB_MCS <- detect_event(res_clim, coldSpells = TRUE)

res_MCS <- ts2clm(SACTN_SB, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 10)
SB_MCS <- detect_event(res_clim, coldSpells = TRUE)

res_clim <- ts2clm(SACTN_SP, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 10)
SP_MCS <- detect_event(res_clim, coldSpells = TRUE)

res_clim <- ts2clm(SACTN_HB, climatologyPeriod = c("1974-01-01", "2005-10-19"),
                   pctile = 10)
HB_MCS <- detect_event(res_clim, coldSpells = TRUE)
```

## Upwelling events - 30th percentile used as a threshold to detect upwellling events

```{r}
res_clim <- ts2clm(SACTN_PN, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 30)
PN_upwelling <- detect_event(res_clim)

res_clim <- ts2clm(SACTN_LB, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 30)
LB_MCS <- detect_event(res_clim)

res_MCS <- ts2clm(SACTN_SB, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 30)
SB_MCS <- detect_event(res_clim)

res_clim <- ts2clm(SACTN_SP, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 30)
SP_MCS <- detect_event(res_clim)

res_clim <- ts2clm(SACTN_HB, climatologyPeriod = c("1974-01-01", "2005-10-19"),
                   pctile = 30)
HB_MCS <- detect_event(res_clim)
```

# Will have to be repeated for the remotely sensed sites

>>>>

# save(SACTN_US, file = "Data/SACTN_US.RData")
```

@@

```{r}

#' # Or if one wants to calculate MCSs

MCS_func <- function(df){
  res_clim <- ts2clm(df, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 10)
  return(res_clim)
}

PN_MCS <- MCS_func(df = SACTN_PN)
LB_MCS <- MCS_func(df = SACTN_LB)
SB_MCS <- MCS_func(df = SACTN_SB)
SP_MCS <- MCS_func(df = SACTN_SP)

res_clim <- ts2clm(SACTN_HB, climatologyPeriod = c("1974-01-01", "2005-10-19"), # Climatological period differs to the rest
                   pctile = 10)

## Events
MCS_event <- function(df){
  detect <- detect_event(df, coldSpells = TRUE)
  return(detect)
}

PN_MCS_events <- MCS_func(df = PN_MCS)
LB_MCS_events <- MCS_func(df = LB_MCS)
SB_MCS_events <- MCS_func(df = SB_MCS)
SP_MCS_events <- MCS_func(df = SP_MCS)

HB_MCS_events <- detect_event(res_clim, coldSpells = TRUE) # line 118 -
```

## Upwelling events - 30th percentile used as a threshold to detect upwellling events.

```{r}
upwell_func <- function(df){
  res_clim <- ts2clm(df, climatologyPeriod = c("1974-01-01", "2015-12-31"),
                   pctile = 30)
  return(res_clim)
}

PN_upwell <- upwell_func(df = SACTN_PN)
LB_upwell <- upwell_func(df = SACTN_LB)
SB_upwell <- upwell_func(df = SACTN_SB)
SP_upwell <- upwell_func(df = SACTN_SP)

res_clim <- ts2clm(SACTN_HB, climatologyPeriod = c("1974-01-01", "2005-10-19"), # Climatological period differs to the rest
                   pctile = 10)

## Events
upwell_event <- function(df){
  detect <- detect_event(df, minDuration = 2, coldSpells = TRUE)
  return(detect)
}

PN_upwell_events <- MCS_func(df = PN_upwell)
LB_upwell_events <- MCS_func(df = LB_upwell)
SB_upwell_events <- MCS_func(df = SB_upwell)
SP_upwell_events <- MCS_func(df = SP_upwell)

HB_upwell_events <- detect_event(res_clim, minDuration = 2, coldSpells = TRUE) # line 1
```
